Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-12-02 analysis/paper/paper.Rmd
knitted into a html

effort_df = raw_df %>%
  select(event_name,
         site,
         date,
         crew,
         crew_count,
         method,
         equipment,
         start_time:total_effort,
         total_day_effort) %>%
  distinct() %>%
  mutate(across(total_effort,
                ~ . * crew_count)) %>%
  group_by(event_name,
           date) %>%
  summarise(across(total_effort,
                   sum),
            .groups = "drop")

cpue_df = effort_df %>%
  # add how many pikeminnow were caught
  left_join(cmr_df %>%
              group_by(event_name, species, date) %>%
              summarise(n_fish = n(),
                        .groups = "drop")) %>%
  mutate(cpue = n_fish / total_effort)

>>>>

effort_df = raw_df %>%
  select(event_name,
         site,
         date,
         crew,
         crew_count,
         method,
         equipment,
         start_time:total_effort,
         total_day_effort) %>%
  distinct() %>%
  mutate(across(total_effort,
                ~ . * crew_count)) %>%
  group_by(event_name,
           date) %>%
  summarise(across(c(total_effort,
                     crew_count),
                   sum),
            .groups = "drop")

cpue_df = effort_df %>%
  # add how many pikeminnow were caught
  left_join(cmr_df %>%
              group_by(event_name, species, date) %>%
              summarise(n_fish = n(),
                        n_large_fish = sum(length>=228,
                                           na.rm = T),
                        .groups = "drop")) %>%
  # calculate CPUE a few different ways
  mutate(cpue = n_fish / total_effort,
         cpue_per_day = n_fish / crew_count,
         cpue_large_per_day = n_large_fish / crew_count)
